---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "fig/README-"
)

library(covr)
coverage_detail <- package_coverage(
  function_exclusions = c("\\.onLoad", "^skip")
)
coverage <- percent_coverage(coverage_detail) |>
  round(0)
```


<!-- badges: start -->
[![img](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)
[![R-CMD-check](https://github.com/steffilazerte/renmods/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/steffilazerte/renmods/actions/workflows/R-CMD-check.yaml)
[![Code Coverage: `r coverage`%](https://img.shields.io/badge/code_coverage-`r coverage`%25-green)](#code-coverage)
<!-- badges: end -->


# renmods

An R package to download, import, and filter data from [B.C.’s Environmental Monitoring Data System](https://www2.gov.bc.ca/gov/content/environment/research-monitoring-reporting/monitoring/environmental-monitoring-data-system) (EnMoDs) into R. 'renmods' package replaces 'rems' to support the new data system released in March 2026. 

The EnMoDs dataset is licensed under the [Open Government Licence - British Columbia](https://www2.gov.bc.ca/gov/content?id=A519A56BC2BF44E4A008B33FCF527F61).

### Features
- Download ENMODS data and cache locally
- Simple connections to the ENMODS database, only to as much data as required to speed up load times.


### Installation

```{r install}
#| eval: false
# install.packages("pak") # if not already installed

library(pak)
pkg_install("bcgov/renmods")
```

### Usage

See the [Get Started](https://steffilazerte.github.io/renmods/articles/renmods.html) tutorial for details


### Project Status

Very first stages of development. 

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/renmods/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

## Code Coverage

```{r codecov, echo=FALSE}
# Non-third party coverage idea from Adam H. Sparks
# https://codeberg.org/adamhsparks/epicrop/src/commit/86b79211bfaf4cd51646f23e0ae9a361f23c34e2/README.Rmd#L12
coverage_detail
```

### License

```
Copyright 2026 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
